Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-10 proposal/proposal.tex
Brandon referenced his papers
Updated Web Application section

The subsystem encapsulating server processing will require a review of recognition software and literature. There exists a market for Automatic License Plate Recognition (ALPR) software that relies on Optical Character Recognition (OCR) engines to extract characters. Once an ALPR solution is chosen, it will be necessary to collect a set of test data using the Acquisition Pi to tune the workflow of character extraction. Because the system is being deployed in the metro Denver area, it can be assumed that Colorado plates will make up the majority of license plates the system will detect.

@@

OpenALPR is another C++ library for use with both North American and European plates. This library relies upon two underlying technologies: OpenCV (an open-source computer vision library) and Tesseract OCR (an OCR engine being developed and maintained by Google). The open-source nature of this project make it appealing as it can be immediately integrated without needing to obtain an educational license first. Additionally, the last updates were pushed to the source repository in January. While it is desirable for the software we consider to be relatively up-to-date and maintained, this repository was created only four months ago (November, 2013). Use of such a young library may require a less stable solution than what is practical to work with throughout the course of the semester.

@@

\subsubsection{Interface with Basestation Pi}
The recognition and extraction of license plate characters will not directly interface with the Arduino Fio or Acquisition Pi that takes the images of cars. Instead, it is assumed all communications will come through the Basestation Pi, and that the Basestation Pi will upload received images to the ACMx Linux server.

@@

Once the ACMx server has a plain text representation of the license plate characters, they will be stored in a MySQL database where they can be retrieved and processed by the Web Application subsystem described in Section 2.6.

\subsection{Web Application}
Taylor
From Brandon: I called you out in my section to describe how your subsystem will use the license plate characters I extract from the MySQL database.

@@

\bibitem{parkingWiki} R. Stillwell. (2014). \emph{Parking Sensor Wiki} [Online]. Available: \url{http://github.com/ColoradoSchoolOfMines/parking_sensor/wiki}
% Not sure how to cite this; can someone help?

>>>>

The subsystem encapsulating server processing will require a review of recognition software and literature. There exists a market for Automatic License Plate Recognition (ALPR) software that relies on Optical Character Recognition (OCR) engines to extract characters. \cite{du2013} describes the various methods and features used to extract characters from a license plate. Once an ALPR solution is chosen, it will be necessary to collect a set of test data using the Acquisition Pi to tune the workflow of character extraction. Because the system is being deployed in the Denver metro area, it can be assumed that Colorado plates will make up the majority of license plates the system will detect.

@@

OpenALPR is another C++ library for use with both North American and European plates. This library relies upon two underlying technologies: OpenCV (an open-source computer vision library) and Tesseract OCR (an OCR engine being developed and maintained by Google). The Tesseract OCR Tool is self-sustaining, and relies on included training data. \cite{patel2012} goes into greater detail how Tesseract extracts data from images. The open-source nature of this project make it appealing as it can be immediately integrated without needing to obtain an educational license first. Additionally, the last updates were pushed to the source repository in January. While it is desirable for the software we consider to be relatively up-to-date and maintained, this repository was created only four months ago (November, 2013). Use of such a young library may require a less stable solution than what is practical to work with throughout the course of the semester.

@@

\subsubsection{Interface with Basestation Pi}
The recognition and extraction of license plate characters will not directly interface with the Arduino Fio or Acquisition Pi that takes the images of cars. Instead, it is assumed all communications will come through the Basestation Pi, and that the Basestation Pi will upload received images to the ACMx Linux server (See section 2.6.1 about the HTTP interface).

@@

Once the ACMx server has a plain text representation of the license plate characters, they will be stored in a MySQL database, along with a timestamp and lot id, where they can be retrieved and processed by the Web Application subsystem described in Section 2.6.

\subsection{Web Application}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx group already has some protocols in place for collecting and displaying the data from the Magnetometor Fios, we will allow their group to continue the development on that part, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.

\subsubsection{HTTP Interface}
The Raspberry Pi base station will need some way to communicate its data with the web application/MySQL database. The simplest way to meet this need is to create an HTTP interface on the server. We will need this interface to handle requests from the front end of the web application anyway, and so it makes sense to also allow the base station to communicate with our server through HTTP requests. We will create a RESTful HTTP interface that corresponds closely to the database schema and the front-end of the webpage, and the base station will send all its data to the application via the same interface. For example, if an image of a license plate is detected, the base station would send an HTTP POST request to http://acmxlabs.org/parking/license_image (actual urls may change when we start designing the interface), and the server would receive the request and send the image to the ALPR software, as described in section 2.5. When the web application needs to get the data associated with a license plate, it will send an HTTP GET request to http://acmxlabs.org/parking/license_plates/123ABC.

\subsubsection{Viewing License Plate Data}
As mentioned in section 2.5, the license plate imnages will be translated from an image into a string of plain text, and stored in the MySQL database on the ACMx server. One of the main functions of the web interface will be the display of this data to administrators. The page that displays the license plate data will have a simple interface which will allow administrators to filter the data by date/time, lot, and license plate number. For example, an administrator should be able to type in a specific license plate number and see all the dates/times that plate has been seen, and in which lot. Alternatively, an admin will be able to enter a date range and lot(s) and see all the license plates that entered/exited the lot(s) during that date range. For now we are only interested in a proof-of-concept type interface that shows that we have the capability to display the collected plate data in a useful format; in the future it could be incredibly useful to cross reference our data with the campus parking department's database to check if a car has entered a lot without a permit.

\subsubsection{Validating and Adjusting Lot Capacity Data}
We expect that our first deployment of this system may not be 100\% accurate at detecting all vehicles that enter and exit lots. Therefore, as mentioned in section 2.4, we will be collecting periodic overhead images from a camera mounted on the base station Raspberry Pi. These images will serve as a visual representation of how many cars are actually in the parking lot at the time the image was taken. Administrators should be able to periodically compare this image to the collected data from the sensor network to make sure the numbers being computed by the network accurately represent the number of cars in the lot. As previously mentioned, the deployment of this project will only be on two campus parking lots, and we may only have one overhead camera to start off with, although ideally we would have two - one for each lot. The web interface will allow administrators to pull up the image for any lot with an overhead camera and see the numbers for that lot right next to the image. If any discrepancies are found, the administrator should be able to overwrite the count in the database to reflect reality. This interface will be extremely useful in helping us to calibrate the system. For example, if the sensors are consistently reporting less cars in the lot than the image shows, we can fine-tune the collection process to make sure fewer cars slip through unnoticed. Future work in this area will include an automated version of this process, where a computer program will compare the image to the sensed data and make any necessary corrections.

\subsubsection{User Accounts}
As the site currently stands, there is no way to restrict certain data to administrators. We would like to create a simple user log-in system that allows general users to view the main parts of the site (maps of lots, state of each lot, stats and trends) without having to log in, and only allows access to the administrator side of the site (2.6.1 and 2.6.2, among other parts) if the user has a valid administrator username and password. This part of the project will be to add this simple security system to the site, and to create an administrator interface that allows top administrators to create, update, and delete other administrators.

@@

\bibitem{parkingWiki} R. Stillwell. (2014). \emph{Parking Sensor Wiki} [Online]. Available: \url{http://github.com/ColoradoSchoolOfMines/parking_sensor/wiki}
